Browsing the Web of Factual Claims

### 2008-09-19 papers/web_of_ideas/web_of_ideas.tex
State before Beth changes. Largely just reference fixing.

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage{wrapfig}
% \usepackage{picins}
% \usepackage{floatflt}
\usepackage[pdftex]{hyperref}
\hypersetup{%
pdftitle={Browsing the Web of Factual Claims},
pdfauthor={Beth Trushkowski and Rob Ennals},
pdfkeywords={CSCW, sensemaking, web, browsers, collaboration, mind mapping},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

@@

The difficulty of finding correct information on the web has been discussed a lot recently. Tim Berners Lee has expressed concern about the difficulty that people face discerning whether information on the web is true~\cite{bbcwebwarning}. Many people have also voiced concerns about how easily people can subvert Wikipedia to give peolpe false information~\cite{wikifalse}. Several commentators have observed that there is a Media Echo Chamber effect~\cite{echochamber,echochamber2} in which news sources report claims that they have heard from other news sources, despite the fact that these claims may be misleading or untrue. If a user only reads news sources from a particular group then they may only be exposed to the views of that group and may not be aware that opposing views exist unless they actively seek them.

Part of the problem is that conventional web browsing tools require the user to browse by looking at pages, when it is often not the pages themselves that the user is interested in but the factual claims contained within them. While a web page will typically contain links to other articles, these typically only reference a small proportial of the other pages that discuss the topic, and are unlikely to include sources that disagree with the author. The best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web. The root of the problem is that the web is structured around where knowledge is coming from (pages written by particular authors) rather than what knowledge is about (the ideas contained on the pages). While this makes it easier for add knowledge to the web, it makes it hard for users to collate all the knowledge available on a topic.

@@

The Think Link claim graph is editable by all users, in a manner similar to a wiki. Any user can add new claims, connect existing claims together, and identify snippets on web pages that make specific claims. Collaborative filtering is used to filter out junk or abusive information, while minimizing the danger of politification.

Not everyone will necessarily want a tool like Think Link. Some people may be looking for confirmation of their own points of view rather than information that challenges their beliefs. We hope however that Think Link may be able to make some contribution to helping peolpe find out about other points of view, and help people more easily find the most interest claims about topics they are interested in.

@@

Think Link is very influenced by wikis like Wikipedia~\cite{wikipedia}. Like Think Link, wikis allow users to find information organised by topic rather than author and allow users to collaborate together to bring together all the best information about a topic. Wikipedia's greatest strength is arguably also its greatest weakness. Since anyone can edit Wikipedia, there is always the danger that information one reads may be incorrect~\cite{wikifalse}. Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect,wikicorrect2,wikicorrect3}, but it is difficult to remove the problem entirely. While good Wikipedia articles will often include references to sources for their claims, following all sources to check up all claims can be laborious. Think Link tries to avoid this problem by linking claims back to the original sources that made these claims. Users can thus use the known trustworthiness of the original sources to judge the reliability of a claim.

@@

SpinSpotter~\cite{spinspotter} shares Think Link's goal of allowing users to identify misleading and innaccurate information on web pages that they read. If a user sees a section of text that they think is misleading then they can mark it up, causing it to be highlighted when other users view the same page. While Think Link and SpinSpotter both share the goal of letting users mark up snippets that may be inaccurate, they differ in what they let users find out about such snippets. SpinSpotter allows users to give a textual description of why the snippet is spin and a suggested edit that would make it more accurate. ThinkLink instead connects the snippet to its global claim graph, allowing users to quickly access evidence for and against the truth of the claim. There is alos a difference in the nature of what SpinSpotter and Think Link expect users to mark up. Think Link is interested in evaluating the truth of factual claims, while SpinSpotter also interested in identifying biased phrases (e.g. ``tree hugger'').

Other web annotation systems such as ShiftSpace~\cite{shiftspace}, Stickis~\cite{stickis}, SharedCopy~\cite{sharedcopy}, and Diigo~\cite{diigo} allow people to add their own annotations to existing web pages and view annotations written by other people. Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relavent documents. More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages. We are not aware of any such system that links web pages to a graph of factual claims.

Web clipping tools such as Google Notebook~\cite{googlenotebook}, Scrapbook~\cite{scrapbook}, and Zotero~\cite{zotero} allow one to gather and organize interesting from web pages. Many web clipping tools are also web annotation systems. These tools are designed for gathering and sharing interesting information, rather than for identifying the claims being made, or allowing users to navigate to related claims being made on other sites.

In Vannevir Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them. As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''. Several more recent systems have allowed user to add links to existing pages. ENQUIRE~\cite{enquire} and TrackBack~\cite{trackback} have bidirectional links, allowing one to see the sites that link to a page as well as those that link from it. Everything2~\cite{everything2} links each page to the most popular pages that users viewed at the same time. Think Link's key difference from this work is that it imposes an additional layer of structure, identifying the factual claims that snippets are making and allowing users to browse this graph, rather than just allowing users to specify links between pages.

@@

Much work has been done on the idea of using a graph to represent an argument~\cite{argumentatino,argmas}. Popular argument models include the Toulmin Model~\cite{toulmin}, the Carneades Model~\cite{carneades}, and the IBIS model~\cite{ibis}. Models used for argumentation theory are usually significantly more complex than our simple supports/opposes model, with the result that they provide a more accurate model of the logical argument, at the cost of requiring more skill to assemble. One feature found in some argumentation graphs~\cite{Korb97acognitive} that we may add in the future is the ability to attach a numberical weight (maybe from voting) asserting how much a claim supports or opposes another claim, or how reliable a claim is.

@@

Think Link has a global graph of factual claims that is shared by all users (Figure~\ref{summarygraph}). This graph is managed like a Wiki, allowing any user to add new claims or snippets. As a user browses the web, they can identify snippets that make claims that are interesting or contraversion and link them into the global claim graph.

Think Link is implemented as a FireFox extension~\cite{firefoxextend} and so can be applied to arbitrary websites without requiring them to be aware of Think Link.

@@

\begin{wrapfigure}{r}[0.3cm]{2cm}
\includegraphics[width=2cm]{../screenshots/marginpull_out.png}
\end{wrapfigure}
If the current page contains snippets then a tab appears in the top left corner of the window. The tab contains a lightbulb icon whose color changes according to the nature of the snippets on the page (Figure~\ref{bookmark_icons}) - red if a snippet contains a contentious claim. This allows a user to quickly tell if a page contains something of interest without having to scroll through the whole page. Clicking on the tab opens the margin. The margin provides a summary of all the interesting claims that users have identified on the current page and is designed to mimick the traditional margin notes that readers often write on physical documents~\cite{marginalia}. To emphasise the connection between a margin note and its associated snippet, each margin note is aligned vertically with its snippet and the snippet is highlighted more strongly when the user mouses over the associated margin note.

@@

When designing an interface to this structure, we were faced with two opposing constraints. We needed to be able to clearly view a large number of claims and topics in a small space, and we needed an interface that made it clear that the data was a graph rather than a tree. Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims in a small place. Tree-based outliners such as OmniOutliner~\cite{outliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.

@@

The placement of objects above and below is intended to emphasize the conventional hierachial structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards. A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.

Animation is used throughout the interface to give users a sense of where they are and how the current interface state related to previous states. When a new item is selected, it grows in size and moves to the center. Other items that were already on the screen move from their current locations to their new locations. Other objects appear and disapper by smoothly sliding into or out of view.

@@

To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser toolbar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button (Figure~\ref{createprocess}). This is a similar approach to that taken clipping tools such as Google Notebook~\cite{googlenotebook}.

@@

Since much of Think Link's utility comes from linking snippets together, it is important that to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics. Motivated by this, we designed the claim selection window to make it easier to pick out an existing claim than to create a new one. Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim. To create a new claim, one navigates to a topic that the claim is about, or a claim that the new claim supports or opposes, and then clicks on the (\includegraphics[width=0.3cm]{../images/add.png}) button on the list that one wishes to add the new claim to. For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim. This is an intentionally different model to that used by ad-hoc tag-based~\cite{tags} systems such as Delicious~\cite{delicious} and Flickr~\cite{flickr}. This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected. In practice, it is inevitable that duplicates claims and topics will sometimes be created. When this happens, a user can mark them as being identical using the same techniques used to create supporting and opposing connections.

@@

\begin{itemize}
\item {\bf A server}, written using Ruby, PHP, and MySQL that maintains the claim graph and provides an API that allows this data to be queried and modified
\item {\bf A web UI}, written using Javascript that implements the claim browser
\item {\bf A page enhancement script}, written in Javascript, that augments the page it is run on by highlighting the factual claims made on the page. This script displays the web UI in an iframe to pick or investigate a claim.
\item {\bf A Firefox extension}\cite{firefoxextend}, that inserts the page enhancement script into all pages the user browses to, and provides toolbar and context-menu shortcuts.
\end{itemize}

@@

The source code to Think Link is publicaly available under the Apache license.

@@

For the first study we recruited 12 paid participants. Five were female, seven were male. Their ages ranged from high school age to retired. Our intention was to recruit users who were not experts, but who regularly used the internet to find information. We recruited participants using a posting to the Craigslist~\cite{craigslist} classified advert site. In our advert, we expressed an interest in people who use the internet to gather knowledge, rather than just for tasks such as email or shopping. We filtered participants based on their short answers to questions about how they found, organized, and shared information on the web.

Study sessions took approximately 45 minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link plugin. We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they found interesting and connect those claims to the existing claim graph. For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelyhood that there would be existing claims about the topic they were browsing.

@@

For the second study, we recruited 6 paid participants. Four were female and two were male. Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the semester meant that five of the participants were students. Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviours.

@@

Response was generally positive, with many participants being very keen to use the tool soon. One partipant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed. Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.

@@

Several usability problems were identified with the first version of the tool, causing us to make design changes for the second version. None of these problems re-occured during the second study. We discuss some of these changes in the sections below.

Most participants in the first study, and all participants in the second study were able to use the tool competently. Participants in the second study were able to use Think Link compentently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. Participants said they found the tool ``very intuitive''.

@@

Many users would consistently mark the first paragraph of an article as a snippet. This paragraph would frequently summarise the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.

\subsubsection{Chosing a Claim for a Snippet}

@@

For the second study, we used the interface described in Section~\ref{newsnippet}, which uses the same claim browser interface used for exploring the claim graph. We found that users of this interface had no difficulty distinguishing between claims and topics and were more likely to reuse existing claims and topics. We theorized that part of the reason for increased reuse was that, because users could see the claim graph they were creating, they felt more motivation to keep it ``tidy'' by reusing existing claims.

@@

Several users expressed an interest in being able to mark a claim as contraversial without having to create an opposing claim. One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence. In the future we are planning to implement a social voting system to allow users to say what claims they believe are false and see what claims their friends agreed or disagreed with.

@@

On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or contraversial, and then using an ``append only, collaborative filtering'' model to allow users to collaborate together to structure claims into an argument graph.

@@

\section{Acknowledgements}

>>>>

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage{wrapfig}
% \usepackage{picins}
% \usepackage{floatflt}
\usepackage[pdftex]{hyperref}
\hypersetup{%
pdftitle={Browsing the Web of Factual Claims},
pdfauthor={Beth Trushkowsky and Rob Ennals},
pdfkeywords={CSCW, sensemaking, web, browsers, collaboration, mind mapping},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

@@

The difficulty of finding correct information on the web has been discussed a lot recently. Tim Berners Lee has expressed concern about the difficulty that people face discerning whether information on the web is true~\cite{bbcwebwarning}. Many people have also voiced concerns about how easily people can subvert Wikipedia to give people false information~\cite{wikifalse}. Several commentators have observed that there is a Media Echo Chamber effect~\cite{echochamber,echochamber2} in which news sources report claims that they have heard from other news sources, despite the fact that these claims may be misleading or untrue. If a user only reads news sources from a particular group then they may only be exposed to the views of that group and may not be aware that opposing views exist unless they actively seek them.

Part of the problem is that conventional web browsing tools require the user to browse by looking at pages, when it is often not the pages themselves that the user is interested in but the factual claims contained within them. While a web page will typically contain links to other articles, these typically only reference a small proportion of the other pages that discuss the topic, and are unlikely to include sources that disagree with the author. The best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web. The root of the problem is that the web is structured around where knowledge is coming from (pages written by particular authors) rather than what knowledge is about (the ideas contained on the pages). While this makes it easier for add knowledge to the web, it makes it hard for users to collate all the knowledge available on a topic.

@@

The Think Link claim graph is editable by all users, in a manner similar to a wiki. Any user can add new claims, connect existing claims together, and identify snippets on web pages that make specific claims. Collaborative filtering is used to filter out junk or abusive information, while minimizing the danger of political edit wars.

Not everyone will necessarily want a tool like Think Link. Some people may be looking for confirmation of their own points of view rather than information that challenges their beliefs. We hope however that Think Link may be able to make some contribution to helping people find out about other points of view, and help people more easily find the most interest claims about topics they are interested in.

@@

Think Link is very influenced by wikis like Wikipedia~\cite{wikipedia}. Like Think Link, wikis allow users to find information organized by topic rather than author and allow users to collaborate together to bring together all the best information about a topic. Wikipedia's greatest strength is arguably also its greatest weakness. Since anyone can edit Wikipedia, there is always the danger that information one reads may be incorrect~\cite{wikifalse}. Several projects have attempted to address this problem by tracking sources of edits~\cite{wikicorrect,wikicorrect2,wikicorrect3}, but it is difficult to remove the problem entirely. While good Wikipedia articles will often include references to sources for their claims, following all sources to check up all claims can be laborious. Think Link tries to avoid this problem by linking claims back to the original sources that made these claims. Users can thus use the known trustworthiness of the original sources to judge the reliability of a claim.

@@

SpinSpotter~\cite{spinspotter} shares Think Link's goal of allowing users to identify misleading and inaccurate information on web pages that they read. If a user sees a section of text that they think is misleading then they can mark it up, causing it to be highlighted when other users view the same page. While Think Link and SpinSpotter both share the goal of letting users mark up snippets that may be inaccurate, they differ in what they let users find out about such snippets. SpinSpotter allows users to give a textual description of why the snippet is spin and a suggested edit that would make it more accurate. Think Link instead connects the snippet to its global claim graph, allowing users to quickly access evidence for and against the truth of the claim. There is also a difference in the nature of what SpinSpotter and Think Link expect users to mark up. Think Link is interested in evaluating the truth of factual claims, while SpinSpotter also interested in identifying biased phrases (e.g. ``tree hugger'').

Other web annotation systems such as ShiftSpace.org, Stickis.com, SharedCopy.com, and Diigo.com allow people to add their own annotations to existing web pages and view annotations written by other people. Common annotations include commenting on perceived inaccuracies, highlighting interesting passages, or linking to other relevant documents. More generally, tools like WBI~\cite{personalweb} and Mash Maker~\cite{mashmaker} allow arbitrary changes to be made to web pages. We are not aware of any such system that links web pages to a graph of factual claims.

Web clipping tools such as Google Notebook, Scrapbook~\cite{scrapbook}, and Zotero.org allow one to gather and organize interesting from web pages. Many web clipping tools are also web annotation systems. These tools are designed for gathering and sharing interesting information, rather than for identifying the claims being made, or allowing users to navigate to related claims being made on other sites.

In Vannevar Bush's seminal MEMEX article~\cite{memex} he proposed an architecture in which links between documents were established by readers, according to the associations between them. As Bush says: ``It is exactly as though the physical items had been gathered together from widely separated sources and bound together to form a new book''. Several more recent systems have allowed user to add links to existing pages. ENQUIRE~\cite{weavingtheweb} and TrackBack~\cite{trackback} have bidirectional links, allowing one to see the sites that link to a page as well as those that link from it. Everything2.com links each page to the most popular pages that users viewed at the same time. Think Link's key difference from this work is that it imposes an additional layer of structure, identifying the factual claims that snippets are making and allowing users to browse this graph, rather than just allowing users to specify links between pages.

@@

Much work has been done on the idea of using a graph to represent an argument~\cite{argumentation,argmas}. Popular argument models include the Toulmin Model~\cite{toulmin}, the Carneades Model~\cite{carneades}, and the IBIS model~\cite{ibis}. Models used for argumentation theory are usually significantly more complex than our simple supports/opposes model, with the result that they provide a more accurate model of the logical argument, at the cost of requiring more skill to assemble. One feature found in some argumentation graphs~\cite{Korb97acognitive} that we may add in the future is the ability to attach a numerical weight (maybe from voting) asserting how much a claim supports or opposes another claim, or how reliable a claim is.

@@

Think Link has a global graph of factual claims that is shared by all users (Figure~\ref{summarygraph}). This graph is managed like a Wiki, allowing any user to add new claims or snippets. As a user browses the web, they can identify snippets that make claims that are interesting or controversial and link them into the global claim graph.

Think Link is implemented as a Firefox extension~\cite{firefoxextend} and so can be applied to arbitrary websites without requiring them to be aware of Think Link.

@@

\begin{wrapfigure}{r}[0.3cm]{2cm}
\includegraphics[width=2cm]{../screenshots/marginpull_out.png}
\end{wrapfigure}
If the current page contains snippets then a tab appears in the top left corner of the window. The tab contains a light bulb icon whose color changes according to the nature of the snippets on the page (Figure~\ref{bookmark_icons}) - red if a snippet contains a contentious claim. This allows a user to quickly tell if a page contains something of interest without having to scroll through the whole page. Clicking on the tab opens the margin. The margin provides a summary of all the interesting claims that users have identified on the current page and is designed to mimic the traditional margin notes that readers often write on physical documents~\cite{marginalia}. To emphasize the connection between a margin note and its associated snippet, each margin note is aligned vertically with its snippet and the snippet is highlighted more strongly when the user mouses over the associated margin note.

@@

When designing an interface to this structure, we were faced with two opposing constraints. We needed to be able to clearly view a large number of claims and topics in a small space, and we needed an interface that made it clear that the data was a graph rather than a tree. Dynamically reorganizing graphs such as those used in Vizster~\cite{vizster} and Personal Brain~\cite{thebrain} made the graph structure very clear, but made it difficult to clearly view large numbers of claims in a small place. Tree-based outliners such as OmniOutliner~\cite{omnioutliner} made it easy to view large numbers of related claims, but made it difficult to present an impression of the data being a graph rather than a tree.

@@

The placement of objects above and below is intended to emphasize the conventional hierarchical structuring of an argument graph, with topics going upwards and arguments for and against a claim going downwards. A user can navigate down to get to explore why a claim may or may not be true, or navigate up to find out about more general topics, or claims that the selected claim supports or opposes.

Animation is used throughout the interface to give users a sense of where they are and how the current interface state related to previous states. When a new item is selected, it grows in size and moves to the center. Other items that were already on the screen move from their current locations to their new locations. Other objects appear and disappear by smoothly sliding into or out of view.

@@

To create a new snippet, the user selects the text to be included and then either clicks on the ``new snippet'' button on the browser tool bar, or selects the ``new snippet'' option from the context menu that appears when they click the right mouse button (Figure~\ref{createprocess}). This is a similar approach to that taken clipping tools such as Google Notebook.

@@

Since much of Think Link's utility comes from linking snippets together, it is important that to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics. Motivated by this, we designed the claim selection window to make it easier to pick out an existing claim than to create a new one. Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim. To create a new claim, one navigates to a topic that the claim is about, or a claim that the new claim supports or opposes, and then clicks on the (\includegraphics[width=0.3cm]{../images/add.png}) button on the list that one wishes to add the new claim to. For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim. This is an intentionally different model to that used by ad-hoc tag-based systems such as Del.icio.us and Flickr.com. This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected. In practice, it is inevitable that duplicates claims and topics will sometimes be created. When this happens, a user can mark them as being identical using the same techniques used to create supporting and opposing connections.

@@

\begin{itemize}
\item {\bf A server}, written using Ruby, PHP, and MySQL that maintains the claim graph and provides an API that allows this data to be queried and modified
\item {\bf A web UI}, written using Javascript that implements the claim browser
\item {\bf A page enhancement script}, written in Javascript, that augments the page it is run on by highlighting the factual claims made on the page. This script displays the web UI in an iframe to pick or investigate a claim.
\item {\bf A Firefox extension}\cite{firefoxextend}, that inserts the page enhancement script into all pages the user browses to, and provides tool bar and context-menu shortcuts.
\end{itemize}

@@

The source code to Think Link is publicly available under the Apache license.

@@

For the first study we recruited 12 paid participants. Five were female, seven were male. Their ages ranged from high school age to retired. Our intention was to recruit users who were not experts, but who regularly used the Internet to find information. We recruited participants using a posting to the Craigslist.org classified advert site. In our advert, we expressed an interest in people who use the Internet to gather knowledge, rather than just for tasks such as email or shopping. We filtered participants based on their short answers to questions about how they found, organized, and shared information on the web.

Study sessions took approximately 45 minutes. Participants were seated at a single-screen workstation with the Firefox browser augmented with the Think Link plugin. We first demonstrated Think Link's interface, and then asked them to browse normally and use Think Link to identify snippets that made claims they found interesting and connect those claims to the existing claim graph. For the first half of the study, we asked them to constrain their browsing to political news articles, to increase the likelihood that there would be existing claims about the topic they were browsing.

@@

For the second study, we recruited 6 paid participants. Four were female and two were male. Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the semester meant that five of the participants were students. Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviors.

@@

Response was generally positive, with many participants being very keen to use the tool soon. One participant said ``I can see myself getting addicted to this'', and several participants asked as to notify them when it is properly deployed. Most of the participants expressed an interest in using the tool, with some wanting to use it now, and others wanting to use it ``when it is more mature''.

@@

Several usability problems were identified with the first version of the tool, causing us to make design changes for the second version. None of these problems re-occurred during the second study. We discuss some of these changes in the sections below.

Most participants in the first study, and all participants in the second study were able to use the tool competently. Participants in the second study were able to use Think Link competently without it being demonstrated in advance and were able to correctly deduce what the different parts of the interface meant. Participants said they found the tool ``very intuitive''.

@@

Many users would consistently mark the first paragraph of an article as a snippet. This paragraph would frequently summarize the arguments made in the rest of the document document and often made an important claim that other claims in the document supported or provided context for.

\subsubsection{Choosing a Claim for a Snippet}

@@

For the second study, we used the interface described earlier in this paper, which uses the same claim browser interface used for exploring the claim graph. We found that users of this interface had no difficulty distinguishing between claims and topics and were more likely to reuse existing claims and topics. We theorized that part of the reason for increased reuse was that, because users could see the claim graph they were creating, they felt more motivation to keep it ``tidy'' by reusing existing claims.

@@

Several users expressed an interest in being able to mark a claim as controversial without having to create an opposing claim. One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence. In the future we are planning to implement a social voting system to allow users to say what claims they believe are false and see what claims their friends agreed or disagreed with.

@@

On a practical level, Think Link works by allowing users to pick out snippets on pages that make claims that they think are interesting or controversial, and then using an ``append only, collaborative filtering'' model to allow users to collaborate together to structure claims into an argument graph.

@@

\section{Acknowledgments}
